%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{SR. SOFTWARE ENGINEER \textbf{(JAVA/SPRING/DART)}} % Job title
{Level Up Trading Contracting W.L.L.} % Organization
{ Doha, Qatar} % Location
{JULY. 2019 - PRESENT} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Responsible to Requirement Analysis, Data analysis, Coding, Design, Report Developing, Maintenance.}
		\item {\textbf{Web: }Spring (Boot, IoC, AOP, ORM, Test, JDBC, Hibernate + JPA, MVC, JDBC, RESTful API}
		\item {\textbf{Mobile: }Flutter}
	\end{cvitems}
}

\cventry
{SOFTWARE ENGINEER \textbf{(JAVA/J2EE/SPRING)}} % Job title
{Orbund LLC.} % Organization
{ Dhaka-1207, Bangladesh} % Location
{April. 2018 - May. 2019} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Built and deployed overall service infrastructure utilizing Java, MYsql,JSP, Servlet, Spring (IoC, AOP, MVC, Transactions), JUnit, Maven, GIT focusing
			on high-availability. }
		\item {Core development with java.}
	\end{cvitems}
}

\cventry
{SOFTWARE ENGINEER \textbf{(JAVA/J2EE/SPRING)}} % Job title
{Shadowhite Ltd.} % Organization
{ Dhaka-1207, Bangladesh} % Location
{August. 2016 - March. 2018} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Built and deployed overall service infrastructure utilizing Java, MYsql, Spring (IoC, AOP, MVC, Transactions), Thymeleaf, JUnit, Maven, GIT focusing
			on high-availability. }
	\end{cvitems}
}


%  \cventry
%    {SOFTWARE ENGINEER (JAVA TRAINER)} % Job title
%    {MSS IT} % Organization
%    { Dhaka-1207, Bangladesh} % Location
%    {August. 2016 - March. 2017} % Date(s)
 %   {
%      \begin{cvitems} % Description(s) of %tasks/responsibilities
%      	\item {As a JAVA(Spring, J2EE, Android) trainer Getting to know the needs of a group in a better way. Researching and planning the lessons to teach the group. }
%      	\item { Organizing the course in such a way that every member of the group gets to learn in an easy way.}
%      	\item {Applies knowledge of end-user needs and issues to assist other ITS staff with design of end user interface}
%      \end{cvitems}
%    }
%---------------------------------------------------------
  \cventry
    {Software Engineer \textbf{(JAVA/J2EE/SPRING)}} % Job title
    {Hipertag Solution Ltd.} % Organization
    {Dhaka-1215,Bangladesh} % Location
    { July, 2015 - July, 2016} % Date(s)
    {
      \begin{cvitems}
      	\item {Built and deployed overall service infrastructure utilizing Java, Oracle 12c, Spring (IoC, AOP, MVC, Transactions), Angular JS, JUnit, Maven, GIT focusing on high-availability, fault tolerance, and auto-scaling.}
      	\item {Implemented RESTful API server}
      	\item {JHIPSTER Technology}
      \end{cvitems}
    }
\end{cventries}
