%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects \& Source Code (GIT)}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}
	
	%---------------------------------------------------------
	\begin{itemize}
	
	
	\item \textbf{Multi-vendor Classifed With E-commerce : } Bigest QATAR marketplace. Fully customised marketplace. Java, Spring (IoC, AOP, MVC,thyemleaf, Transactions), JUnit, PostgreSQL, GIT(private) are used to develop this application. For mobile application, We are using Flutter. \\ \textbf{Web : } \underline{https://www.souqdelta.com} \\ \textbf{Mobile : } \underline{https://play.google.com/store/apps/details?id=com.souqdelta.souq\textunderscore delta}
		
		\item \textbf{In-House Projects : } Worked on 3 Government Projects, Question Bank, Events Calendar, Full calendar, Schedule wise calendar, Student profile, Assessment, Assignment, Attendance rounding policy, many types of report etc.
		
		\item \textbf{Solution Bank(Market place for theme,code, Networking Tools) : }you can buy and sell code or theme, show live preview of a theme or code , profile management and many things.Java, Spring (IoC, AOP, MVC,thyemleaf, Transactions), JUnit, MYSQL, GIT(private) are used to develop this application.
		
		
		\item \textbf{Question Paper Management System : }I developed Question paper management system which is used by \textsc{Bangladesh Technical Education Board (BTEB)} and funded by World bank with STEP project. JHIPSTER technologies like Java, Oracle 12c, Spring (IoC, AOP, MVC, Transactions), Angular JS, JUnit, Maven, GIT are used to develop this module.
		
		
		\item \textbf{Asset Management System :} I developed Asset Management System which is used by \textsc{Directorate Of Technical Education (DTE)} and funded by World bank with STEP project. Java, Oracle 12c, Spring (IoC, AOP, MVC), Angular JS, JUnit, Maven, GIT are used to develop this module.
		
		\item \textbf{Recruitment Management System : } This web application solve all of complexity in a recruitment process. Java, Spring (IoC, AOP, MVC, Transactions), Angular JS, JUnit, MYSQL GRUNT, GIT are used to develop this application.\\ \underline{https://github.com/MHbappy/recruitmentFront}
		
		\item \textbf{Electric Music Shop : } you can buy, listen to song from this site.Java, Spring (IoC, AOP, MVC, Transactions), Angular JS, JUnit, MYSQL, GIT are used to develop this application.\underline{https://github.com/MHbappy/ElectricMusicShop}
		
				
				\item \textbf{Electronic Blood Bank : } With NO SQL technology like google firebase is used to develop this Android Mobile Application.\\ \underline{https://github.com/MHbappy/EBBB}
				
				\item \textbf{Electronic Quran : } Integrated full QURAN  and has a search option with special key and much more.\\ \underline{https://github.com/MHbappy/Quran}
		
		
		
	\end{itemize}
\end{cvparagraph}

